---
output: html_document
editor_options: 
  chunk_output_type: console
---
Outlier Analysis
===

> Code by Lotte van Boheemen

The below code will do the following:
- Look at basic distribution of the data  
- Define what an outlier is  
- Calculate number of outliers based on sliding window, where window size is set to a certain number of bases
- Print out actual window size in bases (between first and last SNP in window)
- Print out window size in SNPs (important if window length is limiting factor)
- Print out number of outliers in SNPs
- Plot distribution of outliers and actual window sizes within each provided data set (ranges)


```{r,include=FALSE}
library("tidyverse")

```

---

**Read data**

Refgenome_data.txt is a file containing all the contigs of the reference genome, so also regions in which no SNPs are called
```{r}
cdata <- read.table("refgenome_data.txt",header=T)

#xtx_na contains xtx values averaged over 3 independent (different root) Bayenv2 runs using .5M iterations, for North-American sampling locations only
xdat_all <- read.table("xtx_all_ddgbs.txt",header=T)

xdat_na <- read.table("xtx_na_ddgbs.txt",header=T)
xdat_eu <- read.table("xtx_eu_ddgbs.txt",header=T)
xdat_au <- read.table("xtx_au_ddgbs.txt",header=T)

loci50 <- read_csv("locinames.csv")
```


Add contig length information to xtx data by combining matrices {dplyr}
```{r}
x_all <- left_join(xdat_all,cdata,by="contig")
x_all$contig <- as.factor(x_all$contig)

x_na <- left_join(xdat_na,cdata,by="contig")
x_na$contig <- as.factor(x_na$contig)

x_eu <- left_join(xdat_eu, cdata,by="contig")
x_eu$contig<-as.factor(x_eu$contig)

x_au <- left_join(xdat_au, cdata,by="contig")
x_au$contig <- as.factor(x_au$contig)
```

Subset for 50% missing data
```{r}
x_all50 <- left_join(loci50, x_all, by = c("contig", "location"))
x_na50 <- left_join(loci50, x_na, by = c("contig", "location"))
x_eu50 <- left_join(loci50, x_eu, by = c("contig", "location"))
x_au50 <- left_join(loci50, x_au, by = c("contig", "location"))

  
```

---  

Outlier window where slide is based on position on the contig (so not SNP).

```{r}
#window length in bases
win.length <- 1000
# slide in bases
slide <- 1000

outlier.window <- function(data, output, top){

  #identify the top percentile by ranking all the data according to their percentile ranks
  data$myrank<-rank(data$xtx)/length(data$xtx)
  
  # create a vector including names of each contig for which SNPs have been found
  cont <- levels(factor(data$contig)) 
  
  # prepare the space for results to be written to
  results <- data.frame(contig=numeric(),windID= numeric(),win.start=numeric(),win.end = numeric(), current.window = numeric(), num.SNPs = numeric(), num.outlier = numeric(), win.mean = numeric(), rank.mean= numeric() )
  
  SNPinfo <- data.frame(contig=numeric(),location = numeric(), xtx = numeric(), myrank = numeric (), win.start = numeric(), win.end = numeric())
  
  #set index for results, this is the index of window passed threshold
  j <- 1

  #set index for SNPinfo results, where every line is a SNP and all information
  a <- 1
  
  # Loop through each contig, stop the loop at the final contig
  for(k in 1:length(cont)){
    
    data2 = data[data$contig==cont[k],]
    data2_all = x_all[x_all$contig==cont[k],]
    
    if(nrow(data2_all)>0){
      
    wID = 1 
    win.start = as.numeric(data2_all$location[[1]])
    last.loc <- as.numeric(max(data2$location))
    
    while(win.start <= last.loc){
   
      win.end = win.start + slide - 1
      wind = data2[which(data2$location>=win.start&data2$location<=win.end),]
      
      if(nrow(wind) > 0){

      # calculate the number of SNPs in the window
      numSNP <- as.numeric(nrow(wind))
      current.window = as.numeric(max(wind$location)- min(wind$location))
      num.outlier <- sum(wind$myrank >= top)
      win.mean <- mean(wind$xtx)
      rank.mean <- mean(wind$myrank)
      
      results[j, ] <- c(cont[k], wID,win.start,win.end,current.window, numSNP, num.outlier, win.mean, rank.mean)
      
      j = j + 1
      # create seperate file with info for every SNP

      for(b in 1:nrow(wind)){
        SNPinfo[a,] <- c(cont[k], wind$location[b], wind$xtx[b],wind$myrank[b], win.start, win.end)
        a <- a + 1
      }
      }
      print(c(a,k, wID))
      win.start = win.start + slide
      wID = wID + 1
      
  }## window
    }
      print(k)
} ## contig

   write.table(results, file = output) 
   temp <- paste0(output,"_SNPinfo")
   write.table(SNPinfo, file = temp)
}
```

Call function for the different datasets
```{r}
outlier.window(x_na50, "xtxna_1000-1000_top99_50miss_allwinds",.99)
outlier.window(x_eu50, "xtxeu_1000-1000_top99_50miss_allwinds",.99)
outlier.window(x_au50, "xtxau_1000-1000_top99_50miss_allwinds",.99)
outlier.window(x_all50, "xtxall_1000-1000_top99_50miss_allwinds",.99)
```

  
##END SCRIPT###