---
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r, include=F}
library(gdata)
library(dplyr)
```

```{r}
#get full genome data for 10% SNP call rate
cdata <- read.table("rawfiles/refgenome_data.txt",header=T)
xdat_all <- read.table("rawfiles/xtx_all_ddgbs.txt",header=T)
x_all <- left_join(xdat_all,cdata,by="contig")
x_all$contig <- as.factor(x_all$contig)
```


```{r}
setwd("/Users/lottevanboheemen/Documents/Monash/PhD/Analyses/Data/gcta_50miss_perrange/NAEU/")
loci <- read.table("locinamesNAEU", header=F)
colnames(loci) = c("contig", "location")

branches <- cbind(loci, read.table("branches.mlma", header=T))
dich <- cbind(loci, read.table("dich.mlma", header=T))
fitall <- cbind(loci, read.table("fitall.mlma", header=T))
flstart <- cbind(loci, read.table("flstart.mlma", header=T))
inflx <- cbind(loci, read.table("inflx.mlma", header=T))
malewt = cbind(loci, read.table("malewt.mlma", header=T))
maxslope <- cbind(loci, read.table("maxslope.mlma", header=T))
maxheight <- cbind(loci, read.table("maxheight.mlma", header=T))
stemwd <- cbind(loci, read.table("stemwd.mlma", header=T))
peakarea <- cbind(loci, read.table("peakarea.mlma", header=T))
peaks <- cbind(loci, read.table("peaks.mlma", header=T))
repal <- cbind(loci, read.table("repal.mlma", header=T))
rosho <- cbind(loci, read.table("rosho.mlma", header=T))
seed20 <- cbind(loci, read.table("seed20.mlma", header=T))
seedwt <- cbind(loci, read.table("seedwt.mlma", header=T))
sexrat <- cbind(loci, read.table("sexrat.mlma", header=T))
sla <- cbind(loci, read.table("sla.mlma", header=T))
totwt <- cbind(loci, read.table("totwt.mlma", header=T))
trichome <- cbind(loci, read.table("trichome.mlma", header=T))
```


Combine datasets for downstream analyses (package gdata)
```{r}
mlma_all <- gdata::combine( branches, dich,fitall, flstart,inflx,maxslope, peakarea, peaks,  repal, rosho, seed20,  seedwt, sexrat,  sla, totwt, trichome ,maxheight, stemwd, malewt) #combine doesn't work when dplyr is active
#mlma_all <- gdata::combine( branches, dich,fitall, flstart, peakarea, peaks,  repal, rosho,  seedwt, sexrat,  sla, trichome , malewt)
#mlma_all = mlma_all[-which(mlma_all$b=="NaN"),]
mlma_all$myrank = rank(mlma_all$p)/length(mlma_all$p)

branches = mlma_all[which(mlma_all$source=="branches"),]
dich = mlma_all[which(mlma_all$source=="dich"),]
fitall = mlma_all[which(mlma_all$source=="fitall"),]
flstart = mlma_all[which(mlma_all$source=="flstart"),]
malewt = mlma_all[which(mlma_all$source=="malewt"),]
inflx = mlma_all[which(mlma_all$source=="inflx"),]
maxslope = mlma_all[which(mlma_all$source=="maxslope"),]
peakarea = mlma_all[which(mlma_all$source=="peakarea"),]
peaks = mlma_all[which(mlma_all$source=="peaks"),]
repal = mlma_all[which(mlma_all$source=="repal"),]
rosho = mlma_all[which(mlma_all$source=="rosho"),]
seed20 = mlma_all[which(mlma_all$source=="seed20"),]
seedwt = mlma_all[which(mlma_all$source=="seedwt"),]
sexrat = mlma_all[which(mlma_all$source=="sexrat"),]
sla = mlma_all[which(mlma_all$source=="sla"),]
totwt = mlma_all[which(mlma_all$source=="totwt"),]
trichome = mlma_all[which(mlma_all$source=="trichome"),]
maxheight = mlma_all[which(mlma_all$source=="maxheight"),]
stemwd = mlma_all[which(mlma_all$source=="stemwd"),]

```


Window CHECK IF USING P CUT-OFF OR TOP % CUT-OFF
---

```{r}
#window length in bases
win.length <- 1000
# slide in bases
slide <- 1000

outlier.window <- function(data, trait, output, top){ 
  # prepare the space for results to be written to
  results <- data.frame(phen=numeric(), contig=numeric(),windID= numeric(),win.start=numeric(), win.end = numeric(), current.window = numeric(), num.SNPs = numeric(), num.outlier = numeric(), win.mean.pval = numeric(), win.mean.effectsize = numeric())
  SNPinfo <- data.frame(phen=numeric(),contig=numeric(),location = numeric(), effectsize = numeric(), pval=numeric(), myrank=numeric(), win.start = numeric(), win.end = numeric())
  #set index for results, this is the index of window passed threshold
  j <- 1
  #set index for SNPinfo results, where every line is a SNP and all information
  a <- 1
  phendata = data 
  # create a vector including names of each contig for which SNPs have been found
  cont <- levels(factor(phendata$contig)) 
  # Loop through each contig, stop the loop at the final contig
  for(k in 1: length(cont)){
    # vector with bf values for all SNPs in each contig
    b <- phendata$b[which(phendata$contig==cont[k])]
    data2 = phendata[phendata$contig==cont[k],]
    data2_all = x_all[x_all$contig==cont[k],]
     if(nrow(data2_all)>0){
      wID = 1 
      win.start = as.numeric(data2_all$location[[1]])
      last.loc <- as.numeric(max(data2$location))
      
      while(win.start <= last.loc){
        win.end = win.start + slide - 1
        wind = data2[which(data2$location>=win.start&data2$location<=win.end),]
        
        if(nrow(wind) > 0){ # only run for windows with SNPs
          # calculate the number of SNPs in the window
          numSNP <- as.numeric(nrow(wind))
          current.window = as.numeric(max(wind$location)- min(wind$location))
          num.outlier <- sum(wind$myrank >= top)
    
          #num.outlier <- sum(wind$p <= top)
          win.meanp <- mean(wind$p)
          win.meanb <- mean(wind$b)
          
         results[j, ] <- c(trait, cont[k], wID,win.start,win.end,current.window, numSNP, num.outlier, win.meanp,  win.meanb) #p cutoff
    
          j = j + 1
          
          # create seperate file with info for every SNP
          for(b in 1:nrow(wind)){
            SNPinfo[a,] <- c(trait, cont[k], wind$location[b], wind$b[b],wind$p[b],wind$myrank[b], win.start, win.end) # p cutoff
            a <- a + 1
          }
        }
      print(c(a,k, wID))
      win.start = win.start + slide
      wID = wID + 1
  }## window
  }
} ## contig
   write.table(results, file = output) 
   temp <- paste0(output,"_SNPinfo")
   write.table(SNPinfo, file = temp)
}

```

top-cutoff
```{r}
#outlier.window(mlma_all, "gctaall_1000-1000_top99_allwinds", 0.99) #runs too long
#outlier.window(p15_7,"p15_7", "gcta15_7_1000-1000_top99_allwinds", 0.99)
#outlier.window(p17_4,"p17_4", "gcta17_4_1000-1000_top99_allwinds", 0.99)
#outlier.window(p18_3,"p18_3", "gcta18_3_1000-1000_top99_allwinds", 0.99)
#outlier.window(p18_6,"p18_6", "gcta18_6_1000-1000_top99_allwinds", 0.99)
#outlier.window(p18_8,"p18_8", "gcta18_8_1000-1000_top99_allwinds", 0.99)
#outlier.window(p21_5,"p21_5", "gct21_5a_1000-1000_top99_allwinds", 0.99)
#outlier.window(p23_8,"p23_8", "gcta23_8_1000-1000_top99_allwinds", 0.99)
outlier.window(branches,"branches", "gctabranches_1000-1000_top99_allwinds", 0.99)
outlier.window(dich,"dich", "gctadich_1000-1000_top99_allwinds", 0.99)
#outlier.window(femday,"femday", "gctfemdaya_1000-1000_top99_allwinds", 0.99)
outlier.window(fitall,"fitall", "gctafitall_1000-1000_top99_allwinds", 0.99)
outlier.window(flstart,"flstart", "gctaflstart_1000-1000_top99_allwinds", 0.99)
#outlier.window(grodays,"grodays", "gctagrodays_1000-1000_top99_allwinds", 0.99)
outlier.window(inflx,"inflx", "gctainflx_1000-1000_top99_allwinds", 0.99)
outlier.window(malewt,"malewt", "gctamalewt_1000-1000_top99_allwinds", 0.99)
outlier.window(maxslope,"maxslope", "gctamaxslope_1000-1000_top99_allwinds", 0.99)
outlier.window(peakarea,"peakarea", "gctapeakarea_1000-1000_top99_allwinds", 0.99)
outlier.window(peaks,"peaks", "gctapeaks_1000-1000_top99_allwinds", 0.99)
#outlier.window(polday,"polday", "gctapolday_1000-1000_top99_allwinds", 0.99)
#outlier.window(racelength,"racelength", "gctaracelength_1000-1000_top99_allwinds", 0.99)
#outlier.window(racemes,"racemes", "gctaracemes_1000-1000_top99_allwinds", 0.99)
outlier.window(repal,"repal", "gctarepal_1000-1000_top99_allwinds", 0.99)
outlier.window(rosho,"rosho", "gctarosho_1000-1000_top99_allwinds", 0.99)
outlier.window(seed20,"seed20", "gctaseed20_1000-1000_top99_allwinds", 0.99)
#outlier.window(seedtot,"seedtot", "gctaseedtot_1000-1000_top99_allwinds", 0.99)
outlier.window(seedwt,"seedwt", "gctaseedwt_1000-1000_top99_allwinds", 0.99)
outlier.window(sexrat,"sexrat", "gctasexrat_1000-1000_top99_allwinds", 0.99)
#outlier.window(shootwt,"shootwt", "gctashootwt_1000-1000_top99_allwinds", 0.99)
outlier.window(sla,"sla", "gctasla_1000-1000_top99_allwinds", 0.99)
outlier.window(totwt,"totwt", "gctatotwt_1000-1000_top99_allwinds", 0.99)
outlier.window(trichome,"trichome", "gctatrichome_1000-1000_top99_allwinds", 0.99)
outlier.window(maxheight,"maxheight", "gctamaxheight_1000-1000_top99_allwinds", 0.99)
outlier.window(stemwd,"stemwd", "gctastemwd_1000-1000_top99_allwinds", 0.99)
```

In unix:

cat gctastemwd_1000-1000_top99_allwinds | awk 'NR == 1' >  ../gcta_all_1000-1000_top99_allwindsNAEU
for i in gcta*_1000-1000_top99_allwinds; do cat $i | tail -n +2 | cut -d " " -f 2- >> ../gcta_all_1000-1000_top99_allwindsNAEU; done

cat gctastemwd_1000-1000_top99_allwinds_SNPinfo | awk 'NR == 1' >  ../gcta_all_1000-1000_top99_allwinds_SNPinfoNAEU
for i in gcta*_1000-1000_top99_allwinds_SNPinfo; do cat $i | tail -n +2 | cut -d " " -f 2- >> ../gcta_all_1000-1000_top99_allwinds_SNPinfoNAEU; done


Binom
---
```{r}
topcan.binom <- function(dat, output){
  
  ##Update following email Kay 13-7-16: the expected proportion is highly reduced when excluding windows with no outliers from the start. Better to run analyses with these windows and exclude no-outlier windows later on. 
  #sdat <- subset(dat,num.outlier > 0) # exclude windows without outliers
  sdat <- subset(dat,num.SNPs > 1) # exclude windows with less than 2 SNPs

  #sdat <- dat
  set.seed(0)
  nsims <- 10000
  maxn <- max(sdat$num.SNPs)
  n <- seq(0, maxn, by = 1)

  #Calculate the expected frequency of outlier SNPs per number of SNPs in a window:  p = ∑_i(a_i/n_i)  
  totsnp1 <- sum(sdat$num.SNPs)
  totout1 <- sum(sdat$num.outlier)
  expect1 <- (totout1 / totsnp1)

    # calculate quantiles
  sdat$p3 <- qbinom (0.999, sdat$num.SNPs, expect1)

  # Check which windows fall above the expected quantile distribution (for each range): top-candidate-outlier windows
  
  sdat$topcan_q <- (sdat$p3 <= sdat$num.outlier) & (sdat$num.outlier > 1) # change 4-9-16: only call topcan when >1 outlier
  
  coverage <- matrix(NA, nrow=length(n), 1)
  q.upper <- matrix(NA, 1, nrow=length(n))
   
  # simulate y data and 99% quantile
  for(i in 1:length(n)){
    y <- rbinom(nsims, n[i], expect1)
    ul <- qbinom(.999, n[i], expect1)
    q.upper[i,] <- ul

    # move the data into a workable dataframe
    for(j in 1:1){
      sig <- length(y[y/n[i] <= ul[j]])
      coverage[i,j] <- sig/nsims
    }
  }
  
  write.table(sdat, file = output)
  return(subset(sdat, topcan_q == "TRUE"))
  
}
```


```{r}
setwd("/Users/lottevanboheemen/Documents/Monash/PhD/Analyses/Data/gcta_50miss_perrange/")
gcta = read.table("gcta_all_1000-1000_top99_allwindsNAEU", header=T)
topcan.binom(gcta, "sres_gctaall_1000-1000_top99_allwindsNAEU")
gcta_wind <- read.table("sres_gctaall_1000-1000_top99_allwindsNAEU", header=T)
test2_sup <- gcta_wind[which(gcta_wind$topcan_q=="TRUE"),]
write.table(test2_sup, "gcta_1000_top99_supwindNAEU")

```


##END SCRIPT##
===