---
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r}
library("dplyr")
library("tidyr")
library("ggplot2")
library("reshape")#melt
library("car") #Anova
library(gdata)
library(tidyr) #spread
library(fifer)
```

Calculate probability of overlap
---
```{r}
bfna = read.table("sresbfall_na_1000_99_allwind.txt", header=T)
bfna$windID = paste0(bfna$contig,"__",bfna$win.start)
bfna$windIDenv = paste0(bfna$contig,"__",bfna$win.start,"__", bfna$envvar)
bfeu = read.table("sresbfall_eu_1000_99_allwind.txt", header=T)
bfeu$windID = paste0(bfeu$contig,"__",bfeu$win.start)
bfeu$windIDenv = paste0(bfeu$contig,"__",bfeu$win.start,"__", bfeu$envvar)
bfau = read.table("sresbfall_au_1000_99_allwind.txt", header=T)
bfau$windID = paste0(bfau$contig,"__",bfau$win.start)
bfau$windIDenv = paste0(bfau$contig,"__",bfau$win.start,"__", bfau$envvar)

bfna_sup = bfna %>% filter(topcan_q =="TRUE")
bfeu_sup = bfeu %>% filter(topcan_q =="TRUE")
bfau_sup = bfau %>% filter(topcan_q =="TRUE")

xna = read.table("sres1000-1000_na99_allwinds", header=T)
xna$windID = paste0(xna$contig,"__",xna$win.start)
xeu = read.table("sres1000-1000_eu99_allwinds", header=T)
xeu$windID = paste0(xeu$contig,"__",xeu$win.start)
xau = read.table("sres1000-1000_au99_allwinds", header=T)
xau$windID = paste0(xau$contig,"__",xau$win.start)

xna_sup = xna %>% filter(topcan_q =="TRUE")
xeu_sup = xeu %>% filter(topcan_q =="TRUE")
xau_sup = xau %>% filter(topcan_q =="TRUE")

bfn_all = read.table("mbf_1000_99_binnullW.txt", header=T)
xn_all = read.table("mxtx_1000_99_binnullW.txt", header=T)

gcta_allwind = read.table("gcta_all_1000-1000_top99_allwinds", header=T)
gcta_allwind$windID = paste0(gcta_allwind$contig,"__",gcta_allwind$win.start)

gcta = read.table("gcta_1000_top99_supwind", header=T)
gcta$windID = paste0(gcta$contig,"__",gcta$win.start)
```

Do GCTA windows associated with traits show signs of selection
```{r}
xwind_na = select(xna_sup,windID)
xwind_eu = select(xeu_sup,windID)
xwind_au = select(xau_sup,windID)
xwind_all  = rbind(xwind_na, xwind_eu, xwind_au)
wind_alluq = unique(xwind_all)

#all common xtx windows
xallwinds = as.data.frame(intersect(intersect(xna$windID, xeu$windID), xau$windID))
colnames(xallwinds) = "windID"


bwind_na = select(bfna_sup,windID)
bwind_eu = select(bfeu_sup,windID)
bwind_au = select(bfau_sup,windID)
bwind_all  = rbind(bwind_na, bwind_eu, bwind_au)
wind_balluq = unique(bwind_all)

ballwinds = as.data.frame(unique(intersect(intersect(bfna$windID, bfeu$windID), bfau$windID)))
colnames(ballwinds) = "windID"

# phyper(q, m, n, k, lower.tail = FALSE, log.p = FALSE), where q=size of outlier overlap-1; m=number of outlier windows method#1;  #n=(total number shared windows-m); k=number of outlier windows range#2.
phyper(length(intersect(wind_balluq$windID,unique(gcta$windID)))-1 ,nrow((wind_balluq)),  length(intersect(unique(ballwinds$windID), unique(gcta_allwind$windID))) - nrow((wind_balluq)),length(unique(gcta$windID)), lower.tail = F, log.p = FALSE)

```


Based on binom results only
```{r}
length(intersect(bfna$windIDenv,bfeu$windIDenv)) # total number of shared windows over all variables
length(intersect(bfna_sup$windIDenv,bfeu_sup$windIDenv)) # total number of shared outlier windows, env has to be the same but window can be identified with multiple envs

# phyper(q, m, n, k, lower.tail = FALSE, log.p = FALSE), where q=size of outlier overlap-1; m=number of outlier windows range#1;  #n=(total number shared windows-m); k=number of outlier windows range#2.

phyper(length(intersect(bfna_sup$windIDenv,bfeu_sup$windIDenv))-1 ,length(levels(bfna_sup)),  length(intersect(bfna$windIDenv,bfeu$windIDenv)) - length(intersect(bfna_sup$windIDenv,bfeu_sup$windIDenv)), length(levels(bfeu_sup)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(bfna_sup$windIDenv,bfau_sup$windIDenv))-1 ,length(levels(bfna_sup)),  length(intersect(bfna_sup$windIDenv,bfau$windIDenv)) - length(intersect(bfna_sup$windIDenv,bfau_sup$windIDenv)), length(levels(bfau_sup)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(bfeu_sup$windIDenv,bfau_sup$windIDenv))-1 ,length(levels(bfeu_sup)),  length(intersect(bfeu_sup$windIDenv,bfau$windIDenv)) - length(intersect(bfeu_sup$windIDenv,bfau_sup$windIDenv)), length(levels(bfau_sup)), lower.tail = F, log.p = FALSE)

#to check what the cut-off for overlap was:
phyper(1500 ,nrow(bfeu_sup),length(intersect(bfeu_sup$windIDenv,bfau$windIDenv)) - length(intersect(bfeu_sup$windIDenv,bfau_sup$windIDenv)), nrow(bfau_sup), lower.tail = F, log.p = FALSE)

##Number of windows, irrespective of environment associated with
# total number of shared windows identified in any of the environments # total number of shared outlier windows, no rep among env
phyper(length(intersect(bfna_sup$windID,bfeu_sup$windID))-1, length(levels(as.factor(bfna_sup$windID))),  length(intersect(bfna$windID,bfeu$windID)) - length(levels(as.factor(bfna_sup$windID))), length(levels(as.factor(bfeu_sup$windID))), lower.tail = F, log.p = FALSE) #NAEU
phyper(length(intersect(bfna_sup$windID,bfau_sup$windID))-1, length(levels(as.factor(bfna_sup$windID))),  length(intersect(bfna$windID,bfau$windID)) - length(levels(as.factor(bfna_sup$windID))), length(levels(as.factor(bfau_sup$windID))), lower.tail = F, log.p = FALSE) #NAAU
phyper(length(intersect(bfeu_sup$windID,bfau_sup$windID))-1, length(levels(as.factor(bfeu_sup$windID))),  length(intersect(bfeu$windID,bfau$windID)) - length(levels(as.factor(bfeu_sup$windID))), length(levels(as.factor(bfau_sup$windID))), lower.tail = F, log.p = FALSE) #EUAU

##Number of windows xtx
phyper(length(intersect(xna_sup$windID,xeu_sup$windID))-1, length(levels(as.factor(xna_sup$windID))),  length(intersect(xna$windID,xeu$windID)) - length(levels(as.factor(xna_sup$windID))), length(levels(as.factor(xeu_sup$windID))), lower.tail = F, log.p = FALSE) #NAEU
phyper(length(intersect(xna_sup$windID,xau_sup$windID))-1, length(levels(as.factor(xna_sup$windID))),  length(intersect(xna$windID,xau$windID)) - length(levels(as.factor(xna_sup$windID))), length(levels(as.factor(xau_sup$windID))), lower.tail = F, log.p = FALSE) #NAAU
phyper(length(intersect(xeu_sup$windID,xau_sup$windID))-1, length(levels(as.factor(xeu_sup$windID))),  length(intersect(xeu$windID,xau$windID)) - length(levels(as.factor(xeu_sup$windID))), length(levels(as.factor(xau_sup$windID))), lower.tail = F, log.p = FALSE) #EUAU
```

Based on binom and nullw
```{r}
bfn_NA = bfn_all %>% filter(Range=="nat") %>% droplevels()
bfn_EU = bfn_all%>% filter( Range=="EU") %>% droplevels()
bfn_AU = bfn_all%>% filter( Range=="AU")%>% droplevels() 
bfn_bsup_NA = bfn_all%>% filter(qbinom=="yes"& Range=="nat") %>% droplevels()
bfn_bsup_EU = bfn_all%>% filter(qbinom=="yes"& Range=="EU") %>% droplevels()
bfn_bsup_AU = bfn_all%>% filter(qbinom=="yes"& Range=="AU")%>% droplevels() 

bfn_sup_NA = bfn_all%>% filter(binnullw=="yes"& Range=="nat") %>% droplevels()
bfn_sup_EU = bfn_all%>% filter(binnullw=="yes"& Range=="EU") %>% droplevels()
bfn_sup_AU = bfn_all%>% filter(binnullw=="yes"& Range=="AU")%>% droplevels() 

xn_NA = xn_all %>% filter(Range=="nat") %>% droplevels()
xn_EU = xn_all%>% filter( Range=="EU") %>% droplevels()
xn_AU = xn_all%>% filter( Range=="AU")%>% droplevels() 
xn_bsup_NA = xn_all %>% filter(binom=="yes"& Range=="nat") %>% droplevels()
xn_bsup_EU = xn_all%>% filter(binom=="yes"& Range=="EU") %>% droplevels()
xn_bsup_AU = xn_all%>% filter(binom=="yes"& Range=="AU")%>% droplevels() 

xn_sup_NA = xn_all%>% filter(binnullw=="yes"& Range=="nat") %>% droplevels()
xn_sup_EU = xn_all%>% filter(binnullw=="yes"& Range=="EU") %>% droplevels()
xn_sup_AU = xn_all%>% filter(binnullw=="yes"& Range=="AU")%>% droplevels() 
# phyper(q, m, n, k, lower.tail = FALSE, log.p = FALSE), where q=size of outlier overlap-1; m=number of outlier windows range#1;  #n=(total number shared windows-m); k=number of outlier windows range#2.

phyper(length(intersect(bfn_sup_NA$windID,bfn_sup_EU$windID))-1, length(levels(bfn_sup_NA$windID)),  length(intersect(bfna$windID,bfeu$windID)) - length(levels(bfn_sup_NA$windID)), length(levels(bfn_sup_EU$windID)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(bfn_sup_EU$windID,bfn_sup_AU$windID))-1, length(levels(bfn_sup_EU$windID)),  length(intersect(bfeu$windID,bfau$windID)) - length(levels(bfn_sup_EU$windID)), length(levels(bfn_sup_AU$windID)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(bfn_sup_NA$windID,bfn_sup_AU$windID))-1, length(levels(bfn_sup_NA$windID)),  length(intersect(bfna$windID,bfau$windID)) - length(levels(bfn_sup_NA$windID)), length(levels(bfn_sup_AU$windID)), lower.tail = F, log.p = FALSE)

phyper(length(intersect(xn_sup_NA$windID,xn_sup_EU$windID))-1, length(levels(xn_sup_NA$windID)),  length(intersect(xna$windID,xeu$windID)) - length(levels(xn_sup_NA$windID)), length(levels(xn_sup_EU$windID)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(xn_sup_EU$windID,xn_sup_AU$windID))-1, length(levels(xn_sup_EU$windID)),  length(intersect(xeu$windID,xau$windID)) - length(levels(xn_sup_EU$windID)), length(levels(xn_sup_AU$windID)), lower.tail = F, log.p = FALSE)
phyper(length(intersect(xn_sup_NA$windID,xn_sup_AU$windID))-1, length(levels(xn_sup_NA$windID)),  length(intersect(xna$windID,xau$windID)) - length(levels(xn_sup_NA$windID)), length(levels(xn_sup_AU$windID)), lower.tail = F, log.p = FALSE)
```


Window has to have hit in at least 2 methods within a range (based on binom AND nullw)
---
```{r}
bfn_sup_NAall = as.data.frame(levels(as.factor(bfn_sup_NA$windID)))
colnames(bfn_sup_NAall) = "windID"
bfxtx_sup_NA = inner_join(xn_sup_NA, bfn_sup_NAall, by="windID")
bfn_sup_EUall = as.data.frame(levels(as.factor(bfn_sup_EU$windID)))
colnames(bfn_sup_EUall) = "windID"
bfxtx_sup_EU = inner_join(xn_sup_EU, bfn_sup_EUall, by="windID")
bfn_sup_AUall = as.data.frame(levels(as.factor(bfn_sup_AU$windID)))
colnames(bfn_sup_AUall) = "windID"
bfxtx_sup_AU = inner_join(xn_sup_AU, bfn_sup_AUall, by="windID")

bfgcta_sup_NA = inner_join(gcta, bfn_sup_NAall, by="windID")
bfgcta_sup_EU = inner_join(gcta, bfn_sup_EUall, by="windID")
bfgcta_sup_AU = inner_join(gcta, bfn_sup_AUall, by="windID")

xgcta_sup_NA = inner_join(gcta, xn_sup_NA, by="windID")
xgcta_sup_EU = inner_join(gcta, xn_sup_EU, by="windID")
xgcta_sup_AU = inner_join(gcta, xn_sup_AU, by="windID")

bfxtxgcta_sup_NA = select(inner_join(bfxtx_sup_NA, gcta, by="windID"), windID)
bfxtxgcta_sup_EU = select(inner_join(bfxtx_sup_EU, gcta, by="windID"), windID)
bfxtxgcta_sup_AU = select(inner_join(bfxtx_sup_AU, gcta, by="windID"), windID)
```

Test
---

```{r}
#EAA-XTX
phyper(length(intersect(bfxtx_sup_NA$windID,bfxtx_sup_EU$windID))-1, length(levels(as.factor(bfxtx_sup_NA$windID))),  length(intersect(bfna$windID,bfeu$windID)) - length(levels(as.factor(bfxtx_sup_NA$windID))), length(levels(as.factor(bfxtx_sup_EU$windID))), lower.tail = F, log.p = FALSE) #bfxtx_NAEU
phyper(length(intersect(bfxtx_sup_EU$windID,bfxtx_sup_AU$windID))-1, length(levels(as.factor(bfxtx_sup_EU$windID))),  length(intersect(bfeu$windID,bfau$windID)) - length(levels(as.factor(bfxtx_sup_EU$windID))), length(levels(as.factor(bfxtx_sup_AU$windID))), lower.tail = F, log.p = FALSE) #bfxtx_EUAU
phyper(length(intersect(bfxtx_sup_NA$windID,bfxtx_sup_AU$windID))-1, length(levels(as.factor(bfxtx_sup_NA$windID))),  length(intersect(bfna$windID,bfau$windID)) - length(levels(as.factor(bfxtx_sup_NA$windID))), length(levels(as.factor(bfxtx_sup_AU$windID))), lower.tail = F, log.p = FALSE) #bfxtx_NAAU

#EAA-GCTA
phyper(length(intersect(bfgcta_sup_NA$windID,bfgcta_sup_EU$windID))-1, length(levels(as.factor(bfgcta_sup_NA$windID))), length(intersect(intersect(bfna$windID,gcta_allwind$windID),bfeu$windID)) - length(levels(as.factor(bfgcta_sup_NA$windID))), length(levels(as.factor(bfgcta_sup_EU$windID))), lower.tail = F, log.p = FALSE) 
phyper(length(intersect(bfgcta_sup_EU$windID,bfgcta_sup_AU$windID))-1, length(levels(as.factor(bfgcta_sup_EU$windID))),  length(intersect(intersect(gcta_allwind$windID,bfau$windID),bfeu$windID))  - length(levels(as.factor(bfgcta_sup_EU$windID))), length(levels(as.factor(bfgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #bfgcta_EUAU
phyper(length(intersect(bfgcta_sup_NA$windID,bfgcta_sup_AU$windID))-1, length(levels(as.factor(bfgcta_sup_NA$windID))),  length(intersect(intersect(gcta_allwind$windID,bfau$windID),bfna$windID)) - length(levels(as.factor(bfgcta_sup_NA$windID))), length(levels(as.factor(bfgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #bfgcta_NAAU

#xtx-GCTA
phyper(length(intersect(xgcta_sup_NA$windID,xgcta_sup_EU$windID))-1, length(levels(as.factor(xgcta_sup_NA$windID))), length(intersect(intersect(xna$windID,gcta_allwind$windID),xeu$windID)) - length(levels(as.factor(xgcta_sup_NA$windID))), length(levels(as.factor(xgcta_sup_EU$windID))), lower.tail = F, log.p = FALSE) 
phyper(length(intersect(xgcta_sup_EU$windID,xgcta_sup_AU$windID))-1, length(levels(as.factor(xgcta_sup_EU$windID))),  length(intersect(intersect(gcta_allwind$windID,xau$windID),xeu$windID))  - length(levels(as.factor(xgcta_sup_EU$windID))), length(levels(as.factor(xgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #xgcta_EUAU
phyper(length(intersect(xgcta_sup_NA$windID,xgcta_sup_AU$windID))-1, length(levels(as.factor(xgcta_sup_NA$windID))),  length(intersect(intersect(gcta_allwind$windID,xau$windID),xna$windID)) - length(levels(as.factor(xgcta_sup_NA$windID))), length(levels(as.factor(xgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #xgcta_NAAU

#all
phyper(length(intersect(bfxtxgcta_sup_NA$windID,bfxtxgcta_sup_EU$windID))-1, length(levels(as.factor(bfxtxgcta_sup_NA$windID))), length(intersect(intersect(xna$windID,gcta_allwind$windID),xeu$windID)) - length(levels(as.factor(bfxtxgcta_sup_NA$windID))), length(levels(as.factor(bfxtxgcta_sup_EU$windID))), lower.tail = F, log.p = FALSE) 
phyper(length(intersect(bfxtxgcta_sup_EU$windID,bfxtxgcta_sup_AU$windID))-1, length(levels(as.factor(bfxtxgcta_sup_EU$windID))),  length(intersect(intersect(gcta_allwind$windID,xau$windID),xeu$windID))  - length(levels(as.factor(bfxtxgcta_sup_EU$windID))), length(levels(as.factor(bfxtxgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #xgcta_EUAU
phyper(length(intersect(bfxtxgcta_sup_NA$windID,bfxtxgcta_sup_AU$windID))-1, length(levels(as.factor(bfxtxgcta_sup_NA$windID))),  length(intersect(intersect(gcta_allwind$windID,xau$windID),xna$windID)) - length(levels(as.factor(bfxtxgcta_sup_NA$windID))), length(levels(as.factor(bfxtxgcta_sup_AU$windID))), lower.tail = F, log.p = FALSE) #xgcta_NAAU
```

Plot
```{r}
#all
area1 = length(levels(as.factor(bfxtxgcta_sup_NA$windID)))
area2= length(levels(as.factor(bfxtxgcta_sup_EU$windID)))
area3= length(levels(as.factor(bfxtxgcta_sup_AU$windID)))
n12 = length(intersect(bfxtxgcta_sup_NA$windID,bfxtxgcta_sup_EU$windID))
n23 = length(intersect(bfxtxgcta_sup_EU$windID,bfxtxgcta_sup_AU$windID))
n13 = length(intersect(bfxtxgcta_sup_NA$windID,bfxtxgcta_sup_AU$windID))
n123 = length(intersect(intersect(bfxtxgcta_sup_NA$windID,bfxtxgcta_sup_EU$windID), bfxtxgcta_sup_AU$windID))
pdf("~/Documents/Monash/PhD/Analyses/Data/_Graph/venn_bfxtxgcta.pdf")
draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07,margin = 0.2)
dev.off()

#x-gcta
area1 = length(levels(as.factor(xgcta_sup_NA$windID)))
area2= length(levels(as.factor(xgcta_sup_EU$windID)))
area3= length(levels(as.factor(xgcta_sup_AU$windID)))
n12 = length(intersect(xgcta_sup_NA$windID,xgcta_sup_EU$windID))
n23 = length(intersect(xgcta_sup_EU$windID,xgcta_sup_AU$windID))
n13 = length(intersect(xgcta_sup_NA$windID,xgcta_sup_AU$windID))
n123 = length(intersect(intersect(xgcta_sup_NA$windID,xgcta_sup_EU$windID), xgcta_sup_AU$windID))
pdf("~/Documents/Monash/PhD/Analyses/Data/_Graph/venn_xtxgcta.pdf")
draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07,margin = 0.2)
dev.off()

#eaa-gcta
area1 = length(levels(as.factor(bfgcta_sup_NA$windID)))
area2= length(levels(as.factor(bfgcta_sup_EU$windID)))
area3= length(levels(as.factor(bfgcta_sup_AU$windID)))
n12 = length(intersect(bfgcta_sup_NA$windID,bfgcta_sup_EU$windID))
n23 = length(intersect(bfgcta_sup_EU$windID,bfgcta_sup_AU$windID))
n13 = length(intersect(bfgcta_sup_NA$windID,bfgcta_sup_AU$windID))
n123 = length(intersect(intersect(bfgcta_sup_NA$windID,bfgcta_sup_EU$windID), bfgcta_sup_AU$windID))
pdf("~/Documents/Monash/PhD/Analyses/Data/_Graph/venn_eaagcta.pdf")
draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07,margin = 0.2)
dev.off()

#eaa-xtx
area1 = length(levels(as.factor(bfxtx_sup_NA$windID)))
area2= length(levels(as.factor(bfxtx_sup_EU$windID)))
area3= length(levels(as.factor(bfxtx_sup_AU$windID)))
n12 = length(intersect(bfxtx_sup_NA$windID,bfxtx_sup_EU$windID))
n23 = length(intersect(bfxtx_sup_EU$windID,bfxtx_sup_AU$windID))
n13 = length(intersect(bfxtx_sup_NA$windID,bfxtx_sup_AU$windID))
n123 = length(intersect(intersect(bfxtx_sup_NA$windID,bfxtx_sup_EU$windID), bfxtx_sup_AU$windID))
pdf("~/Documents/Monash/PhD/Analyses/Data/_Graph/venn_eaaxtx.pdf")
draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07,margin = 0.2)
dev.off()

```

other plot
```{r}
##ALl windows EAA (repeat among env)
area1 = length(levels(as.factor(bfna$windIDenv)))
area2= length(levels(as.factor(bfeu$windIDenv)))
area3= length(levels(as.factor(bfau$windIDenv)))
n12 = length(intersect(bfna$windIDenv,bfeu$windIDenv))
n23 = length(intersect(bfeu$windIDenv,bfau$windIDenv))
n13 = length(intersect(bfna$windIDenv,bfau$windIDenv))
n123 = length(intersect(intersect(bfna$windIDenv,bfeu$windIDenv), bfau$windIDenv))

draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07, rotation.degree = 270,
margin = 0.2)

##ALl windows EAA (no repeat among env)
area1 = length(levels(as.factor(bfna$windID)))
area2= length(levels(as.factor(bfeu$windID)))
area3= length(levels(as.factor(bfau$windID)))
n12 = length(intersect(levels(as.factor(bfna$windID)),levels(as.factor(bfeu$windID))))
n23 =  length(intersect(levels(as.factor(bfeu$windID)),levels(as.factor(bfau$windID))))
n13 = length(intersect(levels(as.factor(bfna$windID)),levels(as.factor(bfau$windID))))
n123 = length(intersect(intersect(levels(as.factor(bfna$windID)),levels(as.factor(bfeu$windID))), levels(as.factor(bfau$windID))))

draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, col = "transparent", fill = c("cornflowerblue","green","red"),
alpha = 0.50, cex = 1.5, fontface = "bold",cat.cex = 1.5,
cat.pos = 0, cat.dist = 0.07, rotation.degree = 270,
margin = 0.2)



```

```{r}
#Number of common windows among env between ranges bf
dat_bfna = dat_bf %>% filter(range=="na") %>% droplevels()
dat_bfeu = dat_bf %>% filter(range=="eu") %>% droplevels()
dat_bfau = dat_bf %>% filter(range=="au") %>% droplevels()

a = length(intersect(levels(dat_bfna$windID),levels(dat_bfeu$windID))) # number of shared outlier windows
b = length(intersect(levels(dat_bfna$windID),levels(dat_bfau$windID)))
c = length(intersect(dat_bfeu$windID,dat_bfau$windID))
d = length(intersect(intersect(dat_bfna$windID,dat_bfau$windID), dat_bfeu$windID))


bfna = read.table("bfall_na_500-500_bf99", header=T)
bfna$windID = paste0(bfna$contig,"__",bfna$win.start,"__",bfna$win.end )
bfeu = read.table("bfall_eu_500-500_bf99", header=T)
bfeu$windID = paste0(bfeu$contig,"__",bfeu$win.start,"__", bfeu$win.end)
bfau = read.table("bfall_au_500-500_bf99", header=T)
bfau$windID = paste0(bfau$contig,"__",bfau$win.start,"__", bfau$win.end)

# total number of  windows
length(levels(as.factor(bfna$windID))) 
length(levels(as.factor(bfeu$windID))) 
length(levels(as.factor(bfau$windID))) 

# total number of outlier windows
length(levels(as.factor(dat_bfna$windID))) 
length(levels(as.factor(dat_bfeu$windID))) 
length(levels(as.factor(dat_bfau$windID))) 

 length(intersect(bfna$windID,bfeu$windID)) # total number of shared windows
 length(intersect(bfna$windID,bfau$windID)) # total number of shared windows
 length(intersect(bfeu$windID,bfau$windID)) # total number of shared windows
 



 phyper(q, m, n, k, lower.tail = FALSE, log.p = FALSE)

#where q=size of overlap-1; m=number of outlier windows range#1; 
 #n=(total number shared windows-m); k=number of outlier windows range#2.

phyper(735, 3320, 404332 , 2796, lower.tail = F, log.p = FALSE)
phyper(586, 3320, 365600 , 2603, lower.tail = F, log.p = FALSE)
phyper(568, 2797, 368976 , 2603, lower.tail = F, log.p = FALSE)

#to check what the cut-off for overlap was:
phyper(31, 3320, 404332 , 2796, lower.tail = F, log.p = FALSE)
```


Test if number of outlier windows is significantly different between range pairs

```{r}
prop.test(x = c(151, 152 ), n = c(15516, 15378)) #NA vs EU xtx
prop.test(x = c(151, 135 ), n = c(15516, 15090)) #NA vs AU xtx
prop.test(x = c(152, 135 ), n = c(15378, 15090)) #EU vs AU xtx
p.adjust(c(0.9377,0.5127,0.4307), method='fdr')

prop.test(x = c(843, 1161 ), n = c(15516, 15378)) #NA vs EU eaa
prop.test(x = c(843, 952 ), n = c(15516, 15090)) #NA vs AU eaa
prop.test(x = c(1161, 952 ), n = c(15378, 15090)) #EU vs AU eaa
p.adjust(c(5.09e-14,0.001215,2.232e-05), method='fdr')
```


Test number of outlier SNPs and outlier windows and test departures for expected distributions
---

Read data
```{r}
datgl=read.table("bf_all_1000-1000_bf99_allwinds_SNPinfo", header=T)
datna=read.table("bfall_na_1000_bf99_allwinds_SNPinfo", header=T)
dateu=read.table("bfall_eu_1000_bf99_allwinds_SNPinfo", header=T)
datau=read.table("bfall_au_1000_bf99_allwinds_SNPinfo", header=T)
wind_gl = read.table("sresbfall_all_1000_99_allwind.txt", header=T)
wind_na = read.table("sresbfall_na_1000_99_allwind.txt", header=T)
wind_eu = read.table("sresbfall_eu_1000_99_allwind.txt", header=T)
wind_au = read.table("sresbfall_au_1000_99_allwind.txt", header=T)
```



Number of SNPs GL
```{r}
supgl = datgl %>% filter(rank>=0.99) %>% droplevels()
envsnp_gl = count(supgl, envvar)

supgl$SNPID = paste0(supgl$contig,"__", supgl$location)
length(levels(as.factor(supgl$SNPID)))#get only uniq SNPs across env
length(as.factor(supgl$SNPID))#get all outlier SNPs

chisq.test(envsnp_gl[,2])

resultssnp_gl=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envsnp_gl$envvar))){
bin = binom.test(envsnp_gl$n[[i]], sum(envsnp_gl$n),1/length(levels (as.factor (envsnp_gl$envvar))), alternative="greater")
resultssnp_gl[i,1] =  levels(envsnp_gl$envvar)[[i]]
resultssnp_gl[i,2] =  bin$p.value
}
resultssnp_gl$q = p.adjust(resultssnp_gl$pval)
```

Number of SNPs NA
```{r}
supna = datna %>% filter(rank>=0.99) %>% droplevels()
envsnp_na = count(supna, envvar)

supna$SNPID = paste0(supna$contig,"__", supna$location)
length(levels(as.factor(supna$SNPID)))#get only uniq SNPs across env
length(as.factor(supna$SNPID))#get all outlier SNPs

chisq.test(envsnp_na[,2])

resultssnp_na=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envsnp_na$envvar))){
bin = binom.test(envsnp_na$n[[i]], sum(envsnp_na$n),1/length(levels (as.factor (envsnp_na$envvar))), alternative="greater")
resultssnp_na[i,1] =  levels(envsnp_na$envvar)[[i]]
resultssnp_na[i,2] =  bin$p.value
}
resultssnp_na$q = p.adjust(resultssnp_na$pval)
```

Number of SNPs EU
```{r}
supeu = dateu %>% filter(rank>=0.99) %>% droplevels()
envsnp_eu = count(supeu, envvar)

supeu$SNPID = paste0(supeu$contig,"__", supeu$location)
length(levels(as.factor(supeu$SNPID)))#get only uniq SNPs across env
length(as.factor(supeu$SNPID))#get all outlier SNPs

chisq.test(envsnp_eu[,2])

resultssnp_eu=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envsnp_eu$envvar))){
bin = binom.test(envsnp_eu$n[[i]], sum(envsnp_eu$n),1/length(levels (as.factor (envsnp_eu$envvar))), alternative="greater")
resultssnp_eu[i,1] =  levels(envsnp_eu$envvar)[[i]]
resultssnp_eu[i,2] =  bin$p.value
}
resultssnp_eu$q = p.adjust(resultssnp_eu$pval)
```

Number of SNPs AU
```{r}
supau = datau %>% filter(rank>=0.99) %>% droplevels()
envsnp_au = count(supau, envvar)

supau$SNPID = paste0(supau$contig,"__", supau$location)
length(levels(as.factor(supau$SNPID)))#get only uniq SNPs across env
length(as.factor(supau$SNPID))#get all outlier SNPs

chisq.test(envsnp_au[,2])

resultssnp_au=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envsnp_au$envvar))){
bin = binom.test(envsnp_au$n[[i]], sum(envsnp_au$n),1/length(levels (as.factor (envsnp_au$envvar))))
resultssnp_au[i,1] =  levels(envsnp_au$envvar)[[i]]
resultssnp_au[i,2] =  bin$p.value
}
resultssnp_au$q = p.adjust(resultssnp_au$pval)
```


1) Is the distribution of loci among environmental variables different from the expected chi-square distribution within each range?
2) Is the proportion of outliers (out of outlier+non-outlier loci) significantly greater than can be expected from binomial distribution?
---

```{r}
supwind_gl = wind_gl %>% filter(topcan_q=="TRUE") %>% droplevels()
envwind_gl = count(supwind_gl, envvar)
chisq.test(envwind_gl[,2])

supwind_gl$windID = paste(supwind_gl$contig, "__", supwind_gl$win.start)
length(levels(as.factor(supwind_gl$windID)))#get only uniq SNPs across env
length(as.factor(supwind_gl$windID))#get all outlier SNPs

resultsgl=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envwind_gl$envvar))){
bin = binom.test(envwind_gl$n[[i]], sum(envwind_gl$n),1/length(levels (as.factor (envwind_gl$envvar))), alternative="greater")
resultsgl[i,1] =  levels(envwind_gl$envvar)[[i]]
resultsgl[i,2] =  bin$p.value
}
resultsgl$q = p.adjust(resultsgl$pval)

supwind_na = wind_na %>% filter(topcan_q=="TRUE") %>% droplevels()
envwind_na = count(supwind_na, envvar)
chisq.test(envwind_na[,2])

supwind_na$windID = paste(supwind_na$contig, "__", supwind_na$win.start)
length(levels(as.factor(supwind_na$windID)))#get only uniq SNPs across env
length(as.factor(supwind_na$windID))#get all outlier SNPs

resultsna=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envwind_na$envvar))){
bin = binom.test(envwind_na$n[[i]], sum(envwind_na$n),1/length(levels (as.factor (envwind_na$envvar))), alternative="greater")
resultsna[i,1] =  levels(envwind_na$envvar)[[i]]
resultsna[i,2] =  bin$p.value
}
resultsna$q = p.adjust(resultsna$pval)

supwind_eu = wind_eu %>% filter(topcan_q=="TRUE") %>% droplevels()
envwind_eu = count(supwind_eu, envvar)
chisq.test(envwind_eu[,2])

supwind_eu$windID = paste(supwind_eu$contig, "__", supwind_eu$win.start)
length(levels(as.factor(supwind_eu$windID)))#get only uniq SNPs across env
length(as.factor(supwind_eu$windID))#get all outlier SNPs

resultseu=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envwind_eu$envvar))){
bin = binom.test(envwind_eu$n[[i]], sum(envwind_eu$n),1/length(levels (as.factor (envwind_eu$envvar))), alternative="greater")
resultseu[i,1] =  levels(envwind_eu$envvar)[[i]]
resultseu[i,2] =  bin$p.value
}
resultseu$q = p.adjust(resultseu$pval)

supwind_au = wind_au %>% filter(topcan_q=="TRUE") %>% droplevels()
envwind_au = count(supwind_au, envvar)
chisq.test(envwind_au[,2])

supwind_au$windID = paste(supwind_au$contig, "__", supwind_au$win.start)
length(levels(as.factor(supwind_au$windID)))#get only uniq SNPs across env
length(as.factor(supwind_au$windID))#get all outlier SNPs

resultsau=data.frame(envvar=as.numeric(), pval=as.numeric())
for(i in 1:length(levels(envwind_au$envvar))){
bin = binom.test(envwind_au$n[[i]], sum(envwind_au$n),1/length(levels (as.factor (envwind_au$envvar))), alternative="greater")
resultsau[i,1] =  levels(envwind_au$envvar)[[i]]
resultsau[i,2] =  bin$p.value
}
resultsau$q = p.adjust(resultsau$pval)
```

Create table with proportion of outliers per env and expectations for each range
---
```{r}
##Calculate proportion of outlier windows
GL=data.frame(envvar=as.numeric(), prop=as.numeric())
for(i in 1:length(levels(envwind_gl$envvar))){
GL[i,1] =  levels(envwind_gl$envvar)[[i]]
GL[i,2] =  envwind_gl$n[[i]]/sum(envwind_gl$n) 
}

NA.=data.frame(envvar=as.numeric(), prop=as.numeric())
for(i in 1:length(levels(envwind_na$envvar))){
NA.[i,1] =  levels(envwind_na$envvar)[[i]]
NA.[i,2] =  envwind_na$n[[i]]/sum(envwind_na$n) 
}

EU=data.frame(envvar=as.numeric(), prop=as.numeric())
for(i in 1:length(levels(envwind_eu$envvar))){
EU[i,1] =  levels(envwind_eu$envvar)[[i]]
EU[i,2] =  envwind_eu$n[[i]]/sum(envwind_eu$n) 
}

AU=data.frame(envvar=as.numeric(), prop=as.numeric())
for(i in 1:length(levels(envwind_au$envvar))){
AU[i,1] =  levels(envwind_au$envvar)[[i]]
AU[i,2] =  envwind_au$n[[i]]/sum(envwind_au$n) 
}

props = combine(GL, NA., EU, AU)
sprops = cbind(NA., EU$prop, AU$prop, GL$prop)
sprops$envvar <- factor(sprops$envvar, levels = c("Latitude_all", "Longitude_all","alt_all", "bio1_all", "bio2_all", "bio3_all",  "bio4_all", "bio5_all","bio6_all","bio7_all","bio8_all","bio9_all","bio10_all","bio11_all","bio12_all","bio13_all","bio14_all","bio15_all","bio16_all","bio17_all","bio18_all","bio19_all"))


##95% CI (one-sided test)
#P = 0.05 # see Yeaman et al 2016

r95gl = data.frame(envvar=as.numeric(), prop=as.numeric(), source= numeric())
for(i in 1:length(levels(envwind_gl$envvar))){
r95gl[i,1] =  levels(envwind_gl$envvar)[[i]]
p = mean(GL$prop)
r95gl[i,2] =   p + c(qnorm(0.95))*sqrt((1/sum(envwind_gl$n))*p*(1-p))
r95gl[i,3] = "GL"
}

r95na = data.frame(envvar=as.numeric(), prop=as.numeric(), source= numeric())
for(i in 1:length(levels(envwind_na$envvar))){
r95na[i,1] =  levels(envwind_na$envvar)[[i]]
p = mean(NA.$prop)
r95na[i,2] =   p + c(qnorm(0.95))*sqrt((1/sum(envwind_na$n))*p*(1-p))
r95na[i,3] = "NA."
}

r95eu = data.frame(envvar=as.numeric(), prop=as.numeric(), source= numeric())
for(i in 1:length(levels(envwind_eu$envvar))){
r95eu[i,1] =  levels(envwind_eu$envvar)[[i]]
p = mean(EU$prop)
r95eu[i,2] =   p + c(qnorm(0.95))*sqrt((1/sum(envwind_eu$n))*p*(1-p))
r95eu[i,3] = "EU"
}

r95au = data.frame(envvar=as.numeric(), prop=as.numeric(), source= numeric())
for(i in 1:length(levels(envwind_au$envvar))){
r95au[i,1] =  levels(envwind_au$envvar)[[i]]
p = mean(AU$prop)
r95au[i,2] =   p + c(qnorm(0.95))*sqrt((1/sum(envwind_au$n))*p*(1-p))
r95au[i,3] = "AU"
}

p95 = rbind(r95gl,r95na, r95eu, r95au)
allprop95 = combine(props, p95)
```

plot
```{r}
allprop95$envvar <- factor(allprop95$envvar, levels = c("Latitude_all", "Longitude_all","alt_all", "bio1_all", "bio2_all", "bio3_all",  "bio4_all", "bio5_all","bio6_all","bio7_all","bio8_all","bio9_all","bio10_all","bio11_all","bio12_all","bio13_all","bio14_all","bio15_all","bio16_all","bio17_all","bio18_all","bio19_all"))
allprop95$source <- factor(allprop95$source, levels = c( "AU","EU", "NA.", "GL" ))

pdf("propoutwind_env_range.pdf", height=3.5, width=7)
ggplot()+
  geom_bar(data = allprop95 %>% filter(source.1=="props"), aes(envvar, prop, fill = source),stat = 'identity',position="dodge") +
  geom_bar(data = allprop95 %>% filter(source.1=="p95"), aes(envvar, prop, fill = source) ,stat = 'identity',position="dodge", alpha=0, size=.1, color="black")  + theme_bw() 
dev.off() 

allprop95_sub = allprop95 %>% filter( envvar %in% c("bio1_all","bio2_all", "bio4_all", "bio8_all", "bio12_all","bio15_all","bio17_all", "alt_all", "Latitude_all", "Longitude_all"))

pdf("propoutwind_env_range_sub.pdf", height=3.5, width=7)
  ggplot()+
  geom_bar(data = allprop95_sub %>% filter(source.1=="props"), aes(envvar, prop, fill = source),stat = 'identity',position="dodge") +
  geom_bar(data = allprop95_sub %>% filter(source.1=="p95"), aes(envvar, prop, fill = source) ,stat = 'identity',position="dodge", alpha=0, size=.1, color="black")                   + theme_bw()                   
dev.off()                             

allprop95_subsub = allprop95 %>% filter(source!="GL"& envvar %in% c("bio1_all","bio2_all", "bio4_all", "bio8_all", "bio12_all","bio15_all","bio17_all", "alt_all", "Latitude_all", "Longitude_all"))

pdf("propoutwind_env_range_subsub.pdf", height=3.5, width=7)
  ggplot()+
  geom_bar(data = allprop95_subsub %>% filter(source.1=="props"), aes(envvar, prop, fill = source),stat = 'identity',position="dodge") +
  geom_bar(data = allprop95_subsub %>% filter(source.1=="p95"), aes(envvar, prop, fill = source) ,stat = 'identity',position="dodge", alpha=0, size=.1, color="black") + theme_bw()                                    
dev.off()                             
  
```


Calculating differences in number of outliers for each environment in pair-wise range comparisons
---
```{r}
dat_snp = cbind(envsnp_gl, envsnp_na$n, envsnp_eu$n, envsnp_au$n)
colnames(dat_snp) = c("env","GL","NA.","EU","AU")
dat_wind = cbind(envwind_gl, envwind_na$n, envwind_eu$n, envwind_au$n)
colnames(dat_wind) = c("env","GL","NA.","EU","AU")

res_snpnaeu = data.frame(env=numeric(), chisq=numeric(),  df=numeric(), p=numeric())
for(i in 1:length(dat_snp$env)){
  tst = prop.test(x= c(dat_snp$NA.[[i]],dat_snp$EU[[i]]), n=c(sum(dat_snp$NA.),sum(dat_snp$EU)))
  res_snpnaeu[i,1] = levels(dat_snp$env)[[i]]
  res_snpnaeu[i,2] = tst$statistic[[1]] #x2 value
  res_snpnaeu[i,3] = tst$parameter[[1]] #df
  res_snpnaeu[i,4] = tst$p.value # pval
}
res_snpnaeu$q = p.adjust(res_snpnaeu$p, method = 'fdr')

res_snpnaau = data.frame(env=numeric(), chisq=numeric(), df=numeric(), p=numeric())
for(i in 1:length(dat_snp$env)){
  tst = prop.test(x= c(dat_snp$NA.[[i]],dat_snp$AU[[i]]), n=c(sum(dat_snp$NA.),sum(dat_snp$AU)))
  res_snpnaau[i,1] = levels(dat_snp$env)[[i]]
  res_snpnaau[i,2] = tst$statistic[[1]] #x2 value
  res_snpnaau[i,3] = tst$parameter[[1]] #df
  res_snpnaau[i,4] = tst$p.value # pval
}
res_snpnaau$q = p.adjust(res_snpnaau$p, method = 'fdr')

res_snpeuau = data.frame(env=numeric(), chisq=numeric(), df=numeric(), p=numeric())
for(i in 1:length(dat_snp$env)){
  tst = prop.test(x= c(dat_snp$EU[[i]],dat_snp$AU[[i]]), n=c(sum(dat_snp$EU),sum(dat_snp$AU)))
  res_snpeuau[i,1] = levels(dat_snp$env)[[i]]
  res_snpeuau[i,2] = tst$statistic[[1]] #x2 value
  res_snpeuau[i,3] = tst$parameter[[1]] #df
  res_snpeuau[i,4] = tst$p.value # pval
}
res_snpeuau$q = p.adjust(res_snpeuau$p, method = 'fdr')

envrangecomp = cbind(res_snpnaeu[,c(1:3,5)],res_snpnaau[,c(2:3,5)],res_snpeuau[,c(2:3,5)])


res_windnaeu = data.frame(env=numeric(), chisq=numeric(), df=numeric(), p=numeric())
for(i in 1:length(dat_wind$env)){
  tst = prop.test(x= c(dat_wind$NA.[[i]],dat_wind$EU[[i]]), n=c(sum(dat_wind$NA.),sum(dat_wind$EU)))
  res_windnaeu[i,1] = levels(dat_wind$env)[[i]]
  res_windnaeu[i,2] = tst$statistic[[1]] #x2 value
  res_windnaeu[i,3] = tst$parameter[[1]] #df
  res_windnaeu[i,4] = tst$p.value # pval
}
res_windnaeu$q = p.adjust(res_windnaeu$p, method = 'fdr')

res_windnaau = data.frame(env=numeric(), chisq=numeric(), df=numeric(), p=numeric())
for(i in 1:length(dat_wind$env)){
  tst = prop.test(x= c(dat_wind$NA.[[i]],dat_wind$AU[[i]]), n=c(sum(dat_wind$NA.),sum(dat_wind$AU)))
  res_windnaau[i,1] = levels(dat_wind$env)[[i]]
  res_windnaau[i,2] = tst$statistic[[1]] #x2 value
  res_windnaau[i,3] = tst$parameter[[1]] #df
  res_windnaau[i,4] = tst$p.value # pval
}
res_windnaau$q = p.adjust(res_windnaau$p, method = 'fdr')

res_windeuau = data.frame(env=numeric(), chisq=numeric(), df=numeric(), p=numeric())
for(i in 1:length(dat_wind$env)){
  tst = prop.test(x= c(dat_wind$EU[[i]],dat_wind$AU[[i]]), n=c(sum(dat_wind$EU),sum(dat_wind$AU)))
  res_windeuau[i,1] = levels(dat_wind$env)[[i]]
  res_windeuau[i,2] = tst$statistic[[1]] #x2 value
  res_windeuau[i,3] = tst$parameter[[1]] #df
  res_windeuau[i,4] = tst$p.value # pval
}
res_windeuau$q = p.adjust(res_windeuau$p, method = 'fdr')

envrangecompwind= cbind(res_windnaeu[,c(1:3,5)],res_windnaau[,c(2:3,5)],res_windeuau[,c(2:3,5)])

```


Calculating the number of loci under selection, and if this is different between ranges
---

```{r}
uni_naeuwind = prop.test(x= c(length(levels(as.factor(supwind_na$windID))),length(levels(as.factor(supwind_eu$SNPID)))), n= c(length(as.factor(supwind_na$windID)), length(as.factor(supwind_eu$windID)))) #outlier wind/total wind, NA-EU
uni_naauwind = prop.test(x= c(length(levels(as.factor(supwind_na$windID))),length(levels(as.factor(supwind_au$SNPID)))), n= c(length(as.factor(supwind_na$windID)), length(as.factor(supwind_au$windID)))) #top 1% SNP/total SNP, NA-EU
uni_euauwind = prop.test(x= c(length(levels(as.factor(supwind_eu$windID))),length(levels(as.factor(supwind_au$SNPID)))), n= c(length(as.factor(supwind_eu$windID)), length(as.factor(supwind_au$windID)))) #top 1% SNP/total SNP, NA-EU

length(levels(as.factor(supwind_na$windID)))/ length((as.factor(supwind_na$windID)))
length(levels(as.factor(supwind_eu$windID)))/ length((as.factor(supwind_eu$windID)))
length(levels(as.factor(supwind_au$windID)))/ length((as.factor(supwind_au$windID)))
length(levels(as.factor(supwind_gl$windID)))/ length((as.factor(supwind_gl$windID)))
       
wind_q = p.adjust(c( uni_naeuwind$p.value,  uni_naauwind$p.value,  uni_euauwind$p.value), method='fdr')

uni_dat = as.data.frame(matrix(ncol=3, nrow=3, byrow=TRUE,data = c(
  uni_naeuwind$statistic[[1]], uni_naeuwind$parameter[[1]], wind_q[1],
  uni_naauwind$statistic[[1]], uni_naauwind$parameter[[1]], wind_q[2],
  uni_euauwind$statistic[[1]], uni_euauwind$parameter[[1]], wind_q[3]
  )))

uni_dat
```

Calculating the number of unique loci under selection, and if this is different between ranges
---

```{r}
uni_naeuwind = prop.test(x= c(length(levels(as.factor(supwind_na$windID))),length(levels(as.factor(supwind_eu$SNPID)))), n= c(length(as.factor(supwind_na$windID)), length(as.factor(supwind_eu$windID)))) #outlier wind/total wind, NA-EU
uni_naauwind = prop.test(x= c(length(levels(as.factor(supwind_na$windID))),length(levels(as.factor(supwind_au$SNPID)))), n= c(length(as.factor(supwind_na$windID)), length(as.factor(supwind_au$windID)))) #top 1% SNP/total SNP, NA-EU
uni_euauwind = prop.test(x= c(length(levels(as.factor(supwind_eu$windID))),length(levels(as.factor(supwind_au$SNPID)))), n= c(length(as.factor(supwind_eu$windID)), length(as.factor(supwind_au$windID)))) #top 1% SNP/total SNP, NA-EU

wind_q = p.adjust(c( uni_naeuwind$p.value,  uni_naauwind$p.value,  uni_euauwind$p.value), method='fdr')

uni_dat = as.data.frame(matrix(ncol=3, nrow=3, byrow=TRUE,data = c(
  uni_naeuwind$statistic[[1]], uni_naeuwind$parameter[[1]], wind_q[1],
  uni_naauwind$statistic[[1]], uni_naauwind$parameter[[1]], wind_q[2],
  uni_euauwind$statistic[[1]], uni_euauwind$parameter[[1]], wind_q[3]
  )))

uni_dat
```

Calculate the number of unique loci compared to the total number selected by each environment between range pairs
---

```{r}
res_snpnaeuau = data.frame(env=numeric(), propNA = numeric(), propEU = numeric(), propAU= numeric(),propGL=numeric(), chisqNAEU=numeric(),  dfNAEU=numeric(), pNAEU=numeric(), qNAEU=numeric(),chisqNAAU=numeric(),  dfNAAU=numeric(), pNAAU=numeric(),qNAAU=numeric(),chisqEUAU=numeric(),  dfEUAU=numeric(), pEUAU=numeric(),qEUAU=numeric() )
for(i in 1:length(levels(supwind_na$envvar))){
  focal_supwindGL = supwind_gl[which(supwind_gl$envvar==levels(supwind_gl$envvar)[i]),]
  othersupwindGL = supwind_gl[which(supwind_gl$envvar!=levels(supwind_gl$envvar)[i]),]
  uniqGL = anti_join(focal_supwindGL, othersupwindGL, by = "windID")
  focal_supwindNA = supwind_na[which(supwind_na$envvar==levels(supwind_na$envvar)[i]),]
  othersupwindNA = supwind_na[which(supwind_na$envvar!=levels(supwind_na$envvar)[i]),]
  uniqNA = anti_join(focal_supwindNA, othersupwindNA, by = "windID")
  focal_supwindEU = supwind_eu[which(supwind_eu$envvar==levels(supwind_eu$envvar)[i]),]
  othersupwindEU = supwind_eu[which(supwind_eu$envvar!=levels(supwind_eu$envvar)[i]),]
  uniqEU = anti_join(focal_supwindEU, othersupwindEU, by = "windID")
  focal_supwindAU = supwind_au[which(supwind_au$envvar==levels(supwind_au$envvar)[i]),]
  othersupwindAU = supwind_au[which(supwind_au$envvar!=levels(supwind_au$envvar)[i]),]
  uniqAU = anti_join(focal_supwindAU, othersupwindAU, by = "windID")
  
  res_snpnaeuau[i,1] = levels(supwind_na$envvar)[[i]]
  res_snpnaeuau[i,2] = nrow(uniqNA)/nrow(focal_supwindNA)
  res_snpnaeuau[i,3] = nrow(uniqEU)/nrow(focal_supwindEU)
  res_snpnaeuau[i,4] = nrow(uniqAU)/nrow(focal_supwindAU)
  res_snpnaeuau[i,5] = nrow(uniqGL)/nrow(focal_supwindGL)
  #NAEEU
  if(nrow(uniqEU)>0 & nrow(uniqNA) > 0){ # only calculate if there are unique windows in each range
  tst = prop.test(x= c(nrow(uniqNA), nrow(uniqEU)), n=c(nrow(focal_supwindNA), nrow(focal_supwindEU)))
  res_snpnaeuau[i,6] = tst$statistic[[1]] #x2 value
  res_snpnaeuau[i,7] = tst$parameter[[1]] #df
  res_snpnaeuau[i,8] = tst$p.value # pval
  }
  
  #NAAU
  if(nrow(uniqAU)>0 & nrow(uniqNA) > 0){ # only calculate if there are unique windows in each range
  tst = prop.test(x= c(nrow(uniqNA), nrow(uniqAU)), n=c(nrow(focal_supwindNA), nrow(focal_supwindAU)))
  res_snpnaeuau[i,10] = tst$statistic[[1]] #x2 value
  res_snpnaeuau[i,11] = tst$parameter[[1]] #df
  res_snpnaeuau[i,12] = tst$p.value # pval
  }
  
  #EUAU
  if(nrow(uniqAU)>0 & nrow(uniqEU) > 0){ # only calculate if there are unique windows in each range
  tst = prop.test(x= c(nrow(uniqEU), nrow(uniqAU)), n=c(nrow(focal_supwindEU), nrow(focal_supwindAU)))
  res_snpnaeuau[i,14] = tst$statistic[[1]] #x2 value
  res_snpnaeuau[i,15] = tst$parameter[[1]] #df
  res_snpnaeuau[i,16] = tst$p.value # pval
  }
}
res_snpnaeuau$qNAEU = p.adjust(res_snpnaeuau$pNAEU, method = 'fdr')
res_snpnaeuau$qNAAU = p.adjust(res_snpnaeuau$pNAAU, method = 'fdr')
res_snpnaeuau$qEUAU = p.adjust(res_snpnaeuau$pEUAU, method = 'fdr')
res_snpnaeuau$env <- factor(res_snpnaeuau$env, levels = c("Latitude_all", "Longitude_all","alt_all", "bio1_all", "bio2_all", "bio3_all",  "bio4_all", "bio5_all","bio6_all","bio7_all","bio8_all", "bio9_all","bio10_all", "bio11_all", "bio12_all","bio13_all","bio14_all","bio15_all","bio16_all","bio17_all","bio18_all","bio19_all"))

write.table(res_snpnaeuau, "prop_uniqwind_envrange")
```

plot
```{r}
res_unq = select(res_snpnaeuau,env,starts_with("prop"))
mres_unq = melt(res_unq)


p95na= p95eu = p95au = 1/length(levels(as.factor(res_unq$env)))
ci95 = select(res_snpnaeuau,env)
ci95$propNA = p95na + c(qnorm(0.95))*sqrt((1/sum(envwind_na$n))*p95na*(1-p95na))
ci95$propEU = p95eu + c(qnorm(0.95))*sqrt((1/sum(envwind_eu$n))*p95eu*(1-p95eu))
ci95$propAU = p95au + c(qnorm(0.95))*sqrt((1/sum(envwind_au$n))*p95au*(1-p95au))
mci95=melt(ci95)

mres_unqci = combine(mres_unq, mci95) #turn dplyr off

mres_unqci$env <- factor(mres_unqci$env, levels = c("Latitude_all", "Longitude_all","alt_all", "bio1_all", "bio2_all", "bio3_all",  "bio4_all", "bio5_all","bio6_all","bio7_all","bio8_all", "bio9_all","bio10_all", "bio11_all", "bio12_all","bio13_all","bio14_all","bio15_all","bio16_all","bio17_all","bio18_all","bio19_all"))
mres_unqci$variable <- factor(mres_unqci$variable, levels = c( "propAU","propEU", "propNA" ))

pdf("prop_uniq_outwind_env_range.pdf", height=3.5, width=7)
  ggplot()+
  geom_bar(data = mres_unqci[which(mres_unqci$source=="mres_unq"),], aes(env, value, fill = variable),stat = 'identity',position="dodge") +
    geom_bar(data = mres_unqci[which(mres_unqci$source=="mci95"),], aes(env, value, fill = variable),stat = 'identity',position="dodge", alpha=0, size=.1, color="black") + theme_bw()  
dev.off()

mres_unqci_subsub = mres_unqci %>% filter(variable!="NA" &env %in% c("bio1_all","bio2_all", "bio4_all", "bio8_all", "bio12_all","bio15_all","bio17_all", "alt_all", "Latitude_all", "Longitude_all"))

pdf("prop_uniq_outwind_env_range_subsub.pdf", height=3.5, width=7)
  ggplot()+
  geom_bar(data = mres_unqci_subsub[which(mres_unqci_subsub$source=="mres_unq"),], aes(env, value, fill = variable),stat = 'identity',position="dodge") +
    geom_bar(data = mres_unqci_subsub[which(mres_unqci_subsub$source=="mci95"),], aes(env, value, fill = variable),stat = 'identity',position="dodge", alpha=0, size=.1, color="black") + theme_bw()  

  dev.off()
```


old
---

```{r}
uni_naeusnp = prop.test(x= c(length(levels(as.factor(supna$SNPID))),length(levels(as.factor(supeu$SNPID)))), n= c(length(as.factor(supna$SNPID)), length(as.factor(supeu$SNPID)))) #top 1% SNP/total SNP, NA-EU
uni_naausnp = prop.test(x= c(length(levels(as.factor(supna$SNPID))),length(levels(as.factor(supau$SNPID)))), n= c(length(as.factor(supna$SNPID)), length(as.factor(supau$SNPID)))) #top 1% SNP/total SNP, NA-EU
uni_euausnp = prop.test(x= c(length(levels(as.factor(supeu$SNPID))),length(levels(as.factor(supau$SNPID)))), n= c(length(as.factor(supeu$SNPID)), length(as.factor(supau$SNPID)))) #top 1% SNP/total SNP, NA-EU

  uni_naeusnp$statistic[[1]], uni_naeusnp$parameter[[1]], snp_q[1],
  uni_naausnp$statistic[[1]], uni_naausnp$parameter[[1]], snp_q[2],
  uni_euausnp$statistic[[1]], uni_euausnp$parameter[[1]], snp_q[3],
  


snp_q = p.adjust(c( uni_naeusnp$p.value,  uni_naausnp$p.value,  uni_euausnp$p.value), method='fdr')

```

```{r}
dat = read.table("windenvrange.txt", header=T)
mdat = melt(dat)
mdat$int  = interaction(mdat$variable, mdat$env)
tst = aov(value~ variable + env, data=mdat)
tst = aov(value~ int, data=mdat)

TukeyHSD(tst)

```

Is this proportion different between range pairs?
```{r}
prop.test(x = c(5568, 8629 ), n = c(19095, 18936)) #NA vs EU eaa
prop.test(x = c(5568, 6655 ), n = c(19095, 17834)) #NA vs AU eaa
prop.test(x = c(8629, 6655 ), n = c(18936, 17834)) #EU vs AU eaa
p.adjust(c(5.09e-14,0.001215,2.232e-05), method='fdr')
```

```{r}
dat=read.table("gcta_all_1000-1000_top99_allwinds_SNPinfo", header=T)
dat2 = dat[which(dat$myrank>=0.99),]
dat2$SNPID = paste0(dat2$contig,"__", dat2$location)
length(levels(as.factor(dat2$SNPID)))

```
Test if the number of outlier windows are allocated similarily along environmental variables between range-paris
```{r}
chisq.test(cbind(dat$NA., dat$EU, dat$AU))
chisq.post.hoc(dat[1:4,2:4], test = c("fisher.test"), popsInRows = FALSE,
control = c("fdr"))

mdat = melt(dat)
mdatnaeu =mdat  %>% filter(variable!="AU") %>% droplevels()
mdatnaau =mdat  %>% filter(variable!="EU") %>% droplevels()
mdateuau = mdat  %>% filter(variable!="NA.") %>% droplevels()

mdat$envrange = interaction(mdat$env,mdat$variable)
tem = glm(value ~ envrange, data=mdat, family = poisson)
summary(tem)
visreg(tem, xvar="env", by="variable")
testInteractions(tem)


fake.glmNAEU = glm(cbind(NA., EU) ~ env, family = binomial(), data = dat)
fake.glmNAAU = glm(cbind(NA., AU) ~ env, family = binomial(), data = dat)
fake.glmEUAU = glm(cbind(EU, AU) ~ env, family = binomial(), data = dat)

fake.lsmNAEU = lsmeans(fake.glmNAEU, "env")
fake.lsmNAAU = lsmeans(fake.glmNAAU, "env")
fake.lsmEUAU = lsmeans(fake.glmEUAU, "env")

plot(fake.lsmNAEU)
plot(fake.lsmNAAU)
plot(fake.lsmEUAU)


```

```{r}
datxtx = read.table("gctabfxtx.txt", header=T)
```



Overlap in BF outliers between GLOBAL and NATIVE dataset, for each environmental variable
```{r}
dat_gcta = dat %>% filter(method=="gcta") %>% droplevels() #the last option will remove the non-used levels 
varl = as.factor(levels(dat_gcta$var))

dat_bf = dat %>% filter(method=="bf") %>% droplevels()
varl_bf = as.factor(levels(dat_bf$var))

```

Number of common windows between traits
```{r}
s = 1
results = data.frame(name = numeric(), count = numeric())
for(j in 1:length(varl)){
  for(i in 1:length(varl)){
    a = dat_gcta %>% filter(var==varl[j])
    b = dat_gcta %>% filter(var==varl[i])
    
    results[s,1] = paste0(varl[j],".", varl[i])
    results[s,2] = length(intersect(a$windID,b$windID))
    
    s = s + 1
  }
}

write.table(results,"countGCTA_GCTA.txt")

```

Number of common windows between traits and bf
```{r}
s = 1
results = data.frame(name = numeric(), count = numeric())
for(j in 1:length(varl_bf)){
  for(i in 1:length(varl)){
    a = dat_bf %>% filter(var==varl_bf[j])
    b = dat_gcta %>% filter(var==varl[i])
    
    results[s,1] = paste0(varl_bf[j],".", varl[i])
    results[s,2] = length(intersect(a$windID,b$windID))
    
    s = s + 1
  }
}

write.table(results,"countGCTA_bf.txt")
```

Number of common windows between traits and bfNA
```{r}
dat_bfna = dat_bf %>% filter(range=="na") %>% droplevels()
varl_bfna = levels(dat_bfna$var)
s = 1
results = data.frame(name = numeric(), count = numeric())
for(j in 1:length(varl_bfna)){
  for(i in 1:length(varl)){
    a = dat_bfna %>% filter(var==varl_bfna[j])
    b = dat_gcta %>% filter(var==varl[i])
    
    results[s,1] = paste0(varl_bfna[j],".", varl[i])
    results[s,2] = length(intersect(a$windID,b$windID))
    
    s = s + 1
  }
}

write.table(results,"countGCTA_bfNA.txt")
```

Number of common windows between traits and bfNA
```{r}
dat_bfeu = dat_bf %>% filter(range=="eu") %>% droplevels()
varl_bfeu = levels(dat_bfeu$var)
s = 1
results = data.frame(name = numeric(), count = numeric())
for(j in 1:length(varl_bfeu)){
  for(i in 1:length(varl)){
    a = dat_bfeu %>% filter(var==varl_bfeu[j])
    b = dat_gcta %>% filter(var==varl[i])
    
    results[s,1] = paste0(varl_bfeu[j],".", varl[i])
    results[s,2] = length(intersect(a$windID,b$windID))
    
    s = s + 1
  }
}

write.table(results,"countGCTA_bfEU.txt")
```

```{r}
dat_bfau = dat_bf %>% filter(range=="au") %>% droplevels()
varl_bfau = levels(dat_bfau$var)
s = 1
results = data.frame(name = numeric(), count = numeric())
for(j in 1:length(varl_bfau)){
  for(i in 1:length(varl)){
    a = dat_bfau %>% filter(var==varl_bfau[j])
    b = dat_gcta %>% filter(var==varl[i])
    
    results[s,1] = paste0(varl_bfau[j],".", varl[i])
    results[s,2] = length(intersect(a$windID,b$windID))
    
    s = s + 1
  }
}

write.table(results,"countGCTA_bfAU.txt")
```



##END SCRIPT###